Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-06-07 paper.tex
Fixing sentence structure.

\begin{itemize}
	\item We find that Pop III stars are forming in halos with a mean mass below $10^{6}$ M$_{\odot}$, which falls well below the M01 relation, until $z=15$, at which point the mean halo mass rises above the M01 relation to a mean value of $3 \times 10^{6}$ M$_{\odot}$ due to the domination of LW radiation produced by metal-enriched stars in the most massive galaxy in the simulation box.
	\item \hh{} self-shielding allows halos below the M01 mass relation, as small as half as previously thought, to cool and form Pop III stars.  Self-shielding creates a disconnect between the LW background and the collapse, resulting in a broad mass distribution of metal-free star forming halos and no strict correlation between the two quantities.
	\item Halos are likely to form multiple Pop III stars. At the instance of Pop III star formation, a halo will have formed a median number of four Pop III stars, up to a maximum of 16.
	\item By the end of the simulation, halos with masses $>10^{7} M_{\odot}$ acquire multiple Pop III stars due to mergers with smaller mass halos, resulting galaxies with young and old metal-free stars. 
\end{itemize}

>>>>

\begin{itemize}
	\item We find that Pop III stars are forming in halos with a mean mass below $10^{6}$ M$_{\odot}$, which falls well below the M01 relation, until $z=15$, at which point the mean halo mass rises above the M01 relation to a mean value of $3 \times 10^{6}$ M$_{\odot}$ due to the domination of LW radiation produced by metal-enriched stars in the most massive galaxy in the simulation box.
	\item \hh{} self-shielding allows halos below the M01 mass relation, as small as half as previously thought, to cool and form Pop III stars.  Self-shielding creates a disconnect between the LW background and the collapse, resulting in a broad mass distribution of metal-free star forming halos and no strict correlation between the two quantities.
	\item Halos are likely to form multiple Pop III stars. At the instance of Pop III star formation, a halo will have formed a median number of four Pop III stars, up to a maximum of 16.
	\item By the end of the simulation, halos with masses $>10^{7} M_{\odot}$ acquire multiple Pop III stars due to mergers with smaller mass halos, resulting in galaxies with young and old metal-free stars. 
\end{itemize}
